Explore tumor cell classification with CellAssign

### 2024-05-23 analyses/cell-type-ewings/template_notebooks/01-marker-genes.Rmd
Apply suggestions from code review
Co-authored-by: Joshua Shapiro <josh.shapiro@ccdatalab.org>
add some messages about skipped plots

```{r}
if(sum(umap_df$gene_expression) == 0){
  has_marker_gene_exp <- FALSE
} else {
  has_marker_gene_exp <- TRUE
}
```

>>>>

```{r}
# test if _any_ marker genes have expression
if(sum(umap_df$gene_expression) == 0){
  has_marker_gene_exp <- FALSE
  message("No marker gene expression detected, so all plots of marker genes will be skipped.")
} else {
  has_marker_gene_exp <- TRUE
}
```

### 2024-05-23 analyses/cell-type-ewings/template_notebooks/02-cellassign.Rmd
add some messages about skipped plots

```{r}
# check if marker gene annotations are present 
if(all(is.na(classifications_df$marker_gene_classification))){
  has_marker_gene <- FALSE
} else {
  has_marker_gene <- TRUE 
}
```

>>>>

```{r}
# check if marker gene annotations are present 
if(all(is.na(classifications_df$marker_gene_classification))){
  has_marker_gene <- FALSE
  message("No annotations were available using only marker gene expression. 
          Any plots comparing CellAssign to marker gene annotation will be skipped.")
} else {
  has_marker_gene <- TRUE 
}
```
